Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

Performing the above for all $i, j \in [k]$ with $i \ne j$ leads to a total time complexity of $O(k^3) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$. A category-2 result tuple $\bm{t}$ may be seen more than once (this can happen if, for example, more than one rectangle in $\bm{t}$ has the same top-edge or the same left-edge). Again, duplicate removal can be achieved at no extra cost asymptotically.

@@

\extraspacing \underline{\em Proof of Statement (1).} Take any $(k-2)$-tuple $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$. Let $r_i$ ($i$ $\in$  $[k-2]$) be the full rectangle of $\bm{t}[i]$. Fix any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$. The segments $h$ and $v$ both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $h \cap v$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

@@

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type1:recur-output}.} Our proof again resorts to the algorithm generate-$\J^*$ in Section~\ref{sec:hv:type1}. As argued in Statement (3) of Lemma~\ref{lmm:hv:type1:properties}, both $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ are non-empty for any $\bm{t} \in \J(R_1',$ $...,R_{k-2}')$. Therefore, in processing this $\bm{t}$, the algorithm adds at least one new tuple to $\J^*$. Hence, $|\J(R_1',...,R_{k-2}')| \le |\J^*|\le |\J(R_1,...,R_{k-2},H,V)| = \out$, where the second inequality used Statement (1) of Lemma~\ref{lmm:hv:type1:properties}.

@@

    \item Then, we explain why $h$ crosses $B_{\bm{t}}$. Because $B_{\bm{t}}\subseteq r'$ and $h$ crosses $r'$ (just proved), no endpoint of $h$ can fall in $B_\bm{t}$. Let us take the y-coordinate $y_h$ of $h$. We will prove that the point $p = (\xleft(B_{\bm{t}}), y_h)$ is on the segment $h \cap B_{\bm{t}}$, suggesting $h\cap B_{\bm{t}} \neq \emptyset$. Once this is done, we can assert that $h$ crosses $B_{\bm{t}}$ (as no endpoint of $h$ falls in $B_\bm{t}$).

>>>>

Performing the above for all $i, j \in [k]$ with $i \ne j$ leads to a total time complexity of $O(k^3) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$. A category-2 result tuple $\bm{t}$ may be seen more than once (this can happen if, for example, more than one rectangle in $\bm{t}$ has the same top-edge). Again, duplicate removal can be achieved at no extra cost asymptotically.

@@

\extraspacing \underline{\em Proof of Statement (1).} Take any $(k-2)$-tuple $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$. Let $r_i$ ($i$ $\in$  $[k-2]$) be the full rectangle of $\bm{t}[i]$. Fix any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$. The segments $h$ and $v$ both cross $B_\bm{t}$, as can be seen directly from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $h \cap v$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

@@

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type1:recur-output}.} Our proof again resorts to the algorithm generate-$\J^*$ in Section~\ref{sec:hv:type1}. By Proposition~\ref{prop:app:hv:type1:help2}, both $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ are non-empty for any $\bm{t} \in \J(R_1',$ $...,R_{k-2}')$. Therefore, in processing this $\bm{t}$, the algorithm adds at least one new tuple to $\J^*$. Hence, $|\J(R_1',...,R_{k-2}')| \le |\J^*|\le |\J(R_1,...,R_{k-2},H,V)| = \out$, where the second inequality used Statement (1) of Lemma~\ref{lmm:hv:type1:properties}.

@@

    \item Then, we explain why $h$ crosses $B_{\bm{t}}$. Because $B_{\bm{t}}\subseteq r'$ and $h$ crosses $r'$ (just proved), no endpoint of $h$ can fall in $B_\bm{t}$. Let us take the y-coordinate $y_h$ of $h$. We will prove that the point $p = (\xleft(B_{\bm{t}}), y_h)$ is on the segment $h$ and is also in $B_{\bm{t}}$, suggesting $h\cap B_{\bm{t}} \neq \emptyset$. Once this is done, we can assert that $h$ crosses $B_{\bm{t}}$ (as no endpoint of $h$ falls in $B_\bm{t}$).
